\textbf{CMCS 818J Project Final Report} \\ Implementing Streaming Authenticated Data Structures

### 2013-03-29 doc/final_report/draft_report.tex

	The core concept that enables the SADS scheme to satisfy its desired goals is a lattice-based hash tree, also known as a Merkle tree.
	In traditional Merkle trees a hash function, such as SHA-1, is used to compute the value of any internal node of the tree.
	SHA-1, and similar hashes, are not homomorphic hash functions; that is, the hash of the sum of two elements is not necessarily the sum of the hash of the individual elements.
	For example, suppose there is a hash $h(x, y)$, a homomorphic hash would satisfy the following relation:
	\begin{equation}
		h(x + y) = h(x) + h(y)
	\end{equation}
	The key to the SADS scheme is Merkle tree using a homomorphic hash function which allows 
	In the case of the SADS scheme, the hash used is one with homomorphic properties allowing each node in the tree to be represented as a sum of parts, including the root of the tree.

@@

		Verification is then done by the verifier in two parts.
		First, each sibling pair is hashed to obtain a digest of their parent.
		That calculated digest must be an equivalent representation of this pair's parent label, obtained from the proof.
		Lastly, the final digest produced by hashing the last pair must be equivalent to the running digest the verifier has been maintaining.
		Shi and Papamanthou \cite{dads} describe the correctness properties in sufficient detail.

@@

	Implementing the SADS scheme was organized as follows.
	The first component to be implemented was the underlying datastructure used by the prover and the mechanisms used by both prover and verifier to support the SADS scheme; mechanisms for determining a node's index in the tree and calculating partial digests for example.
	Then the data structures and mechanisms to support the query phase was added.
	Finally, these two parts were packaged as a library such that another project may leverage the scheme primitive and build applications on top of SADS.

@@

	The next stage was to implement streaming setting in which the Prover and Verifier operate independently while witnessing a common stream of data.
	We wrote a very simple script to simulate such a scenario.
	This script was created as a new project, also using Ruby, and installed the SADS library via the RubyGems command 'gem install --local'.
	We wanted to ensure that the steps we took to use the SADS library in another project were the same or close to what other developers might do when using our library.
	The script takes three parameters to initialize the entire protocol, the security parameter, the upper bound on the size of the stream, and the size of the universe of stream elements.
	The Prover can be initialized from just these three parameter.
	The Verifier is then initialized with parameters provided to it from the Prover, similar to a client-server initialization wherein a client requests a session from a web server and can only proceed once the server grants the client the credentials.
	Finally in this small example, the user is then able to run commands such as "add" which simulates the Prover and Verifier both witnessing some stream element or "query" which simulates a membership query from the Verifier to the Prover.

	The final stage is to implement the simulation across distributed computing infrastructure, that is a Prover and Verifier non-co-located.
	We imagine at least two possibilities for this implementation.
	One possibility could be a web service could be created that plays matchmaker between "needy" clients requesting prover services and "generous" clients wishing to act as a prover.
	Another possibility, similar to the first, is one in which the web service itself acts as a Prover for any client requesting service.
	In either of these scenarios we imagine deploying a server application possibly build in EventMachine or Node.js or some similar framework.
	Some proposed applications include monitoring and verifying of bandwidth charges from an ISP or continuous sensor data.

\section{Looking Forward}
\label{sec:forward}
	\subsection{ Production Quality Libraries }

@@

>>>>

	The core concept that enables the SADS scheme to satisfy its desired goals is a lattice-based hash tree, also known as a Merkle tree.
	In traditional Merkle trees a hash function, such as SHA-1, is used to compute the value of any internal node of the tree.
	SHA-1, and similar hashes, are not homomorphic hash functions; that is, the hash of the sum of two elements is not necessarily the sum of the hash of the individual elements.
	For example, suppose there is a hash $h(x, y)$, a homomorphic hash would satisfy the following relation:
	\begin{equation}
		h(x + y) = h(x) + h(y)
	\end{equation}
	The key to the SADS scheme is Merkle tree using a homomorphic hash function which allows each node in the tree to be represented as a sum of parts, including the root of the tree.

@@

		Verification is then done by the verifier in two parts.
		First, each sibling pair is hashed to obtain a digest of their parent.
		That calculated digest must be an equivalent representation of this pair's parent label, obtained from the proof.
		Lastly, the final digest produced by hashing the last pair must be equivalent to the running digest the verifier has been maintaining.
		Shi and Papamanthou \cite{sads} describe the correctness properties in sufficient detail.

@@

	Implementing the SADS scheme was organized as follows.
	The first component to be implemented was the underlying data structure used by the prover and the mechanisms used by both prover and verifier to support the SADS scheme; mechanisms for determining a node's index in the tree and calculating partial digests for example.
	Then the data structures and mechanisms to support the query phase was added.
	Finally, these two parts were packaged as a library such that another project may leverage the scheme primitive and build applications on top of SADS.

@@

	The next stage was to implement the streaming setting in which the Prover and Verifier operate independently while witnessing a common stream of data.
	We wrote a very simple script to simulate such a scenario.
	This script was created as a new project, also using Ruby, and installed the SADS library via the RubyGems command `gem install --local $<$path to library$>$'.
	We wanted to ensure that the steps we took to use the SADS library in another project were the same as what we would expect other developers to do when using our library.
	The script takes three parameters to initialize the entire protocol, the security parameter, the upper bound on the size of the stream, and the size of the universe of stream elements.
	The Prover can be initialized from just these three parameter.
	The Verifier is then initialized with parameters provided to it from the Prover, similar to a client-server initialization wherein a client requests a session from a web server and can only proceed once the server grants the client the credentials.
	Finally in this small example, the user is then able to run commands such as ``add" which simulates the Prover and Verifier both witnessing some stream element or "query" which simulates a full membership query and response verification between Verifier to the Prover.

	The final stage is to implement the simulation across distributed computing infrastructure, that is, with a Prover and a Verifier which are not co-located.
	We imagine at least two possibilities for this implementation.
	One possibility could be a web service that plays matchmaker between ``needy" clients requesting prover services and ``generous" clients wishing to act as a prover.
	The web service would then facilitate communication between the two parties but would not provide the computational resources to act as either the prover or verifier.
	Another possibility, similar to the first, is one in which the web service itself acts as a Prover for any client requesting service.
	In either of these scenarios we imagine deploying a server application possibly built with EventMachine or Node.js or some other similar web application framework.
	Some proposed applications include monitoring and verifying of bandwidth charges from an ISP or continuous sensor data.

\section{Looking Forward}
\label{sec:forward}

@@

	\subsection{ Production Quality Libraries }
